method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
corrected ANOVA

SubjArousalReg_con[1,1] <- "$Distancing - Distraction$"
SubjArousalReg_con[2,1] <- "$Distancing - Suppression$"
SubjArousalReg_con[3,1] <- "$Distancing - View_{negative}$"
SubjArousalReg_con[4,1] <- "$Distraction - Suppression$"
SubjArousalReg_con[5,1] <- "$Distraction - View_{negative}$"
SubjArousalReg_con[6,1] <- "$Suppression - View_{negative}$"

@@

# figure
FigSubjArousalRegPilot <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

SubjEffort_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distraction"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distraction"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distraction"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distancing"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf)

@@

SubjEffort_con[1,1] <- "$Distancing - Distraction$"
SubjEffort_con[2,1] <- "$Distancing - Suppression$"
SubjEffort_con[3,1] <- "$Distancing - View_{negative}$"
SubjEffort_con[4,1] <- "$Distraction - Suppression$"
SubjEffort_con[5,1] <- "$Distraction - View_{negative}$"
SubjEffort_con[6,1] <- "$Suppression - View_{negative}$"

# Figure to visualize effort ratings
# figure
FigSubjEffortPilot = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")

>>>>

SubjArousalReg_con[1,1] <- "$View_{negative} - Distraction$"
SubjArousalReg_con[2,1] <- "$View_{negative} - Distancing$"
SubjArousalReg_con[3,1] <- "$View_{negative} - Suppression$"
SubjArousalReg_con[4,1] <- "$Distraction - Distancing$"
SubjArousalReg_con[5,1] <- "$Distraction - Suppression$"
SubjArousalReg_con[6,1] <- "$Distancing - Suppression$"

@@

# figure
FigSubjArousalRegPilot <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

SubjEffort_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf)

@@

SubjEffort_con[1,1] <- "$View_{negative} - Distancing$"
SubjEffort_con[2,1] <- "$View_{negative} - Distraction$"
SubjEffort_con[3,1] <- "$View_{negative} - Suppression$"
SubjEffort_con[4,1] <- "$Distraction - Distancing$"
SubjEffort_con[5,1] <- "$Distraction - Suppression$"
SubjEffort_con[6,1] <- "$Distancing - Suppression$"

# Figure to visualize effort ratings
# figure
FigSubjEffortPilot = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
